Summarize twas: chr22

### 2020-08-05 analysis/simulation-multi-ukbchr17to22-gtex.adipose.Rmd
move code-  plot functions

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/sa2_default/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/sa2_default/"
tags <- paste0('20200721-1-', c(2, 4:9))
tagglob <- '20200721-1-*'
tagextr <- '20200721-1-\\d+'
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

```{r getfile function}

get_files <- function(tag, tag2){
  par <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt")
  rpip <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".rPIP.txt")

  gmrash <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt")
  smrash <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt")

  ggwas <- paste0(outputdir, tag, ".exprgwas.txt.gz")
  sgwas <- paste0(outputdir, tag, ".snpgwas.txt.gz")

  gsusie <- paste0(susiedir, tag, ".", tag2, ".L3.susieres.expr.txt")
  ssusie <- paste0(susiedir, tag, ".", tag2, ".L3.susieres.snp.txt")

  return(tibble::lst(par, rpip, gmrash, ggwas, smrash, sgwas, gsusie, ssusie))
}

get_tags <- function(globpattern, extrpattern, tag2){
  lapply(lapply(get_files(globpattern, tag2), Sys.glob), str_extract, pattern = extrpattern)
}
```
# Mr.ash2 parameter estimation

@@

```{r param function}
show_param <- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  parf <- lapply(f, '[[', "par")
  param <- do.call(rbind, lapply(parf, function(x) t(read.table(x))[2:1,]))
  truth <- param[1:(nrow(param)/2)*2-1,]
  est <- param[1:(nrow(param)/2)*2,]
  outdt <- matrix(0, ncol = 2*ncol(param), nrow = nrow(param)/2)
  outdt[,c(1,3,5,7)] <- truth
  outdt[,c(2,4,6,8)] <- est
  outdt <-cbind(1:nrow(outdt),outdt)
  colnames(outdt) <- c("Simulation#", paste0(rep(c("Truth","Est."),4)))
  knitr::kable(outdt) %>%
  kable_styling("striped") %>%
  add_header_above(c(" " = 1, "Gene.pi1" = 2, "Gene.PVE" = 2, "SNP.pi1" = 2, "SNP.PVE" =2))
}
```

@@

# PIP calibration
We run 50 simulations and combine results.
```{r caliplot}
#' s is pip or fdr.
cp_plot <- function(s, ifcausal, mode = c("PIP", "FDR"), main = mode[1]){
  # ifcausal:0,1
  a_bin <- cut(s, breaks= seq(0,1, by=0.1))
  if (mode == "PIP") {
     expected = c(by(s, a_bin, FUN = mean))
     observed = c(by(ifcausal, a_bin, FUN = mean))
  } else if (mode == "FDR"){
     expected = c(by(s, a_bin, FUN = mean))
     observed = 1 - c(by(ifcausal, a_bin, FUN = mean))
  }
  plot(expected, observed, xlim= c(0,1), ylim=c(0,1), pch =19, main = main)
  lines(x = c(0,1), y = c(0,1), col ="red")
}

caliPIP_plot <- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- res[complete.cases(res),]
  res <- rename(res, c("PIP" = "mr.ash_PIP", "pip" = "SUSIE_PIP", "pip.null" = "SUSIE_PIP_null", "pip.w0" = "SUSIE_PIP_w0"))
  par(mfrow=c(1,4), mar=c(5, 6, 4, 1))
  cp_plot(res$mr.ash_PIP, res$ifcausal, main = "Mr.ash PIP")
  cp_plot(res$SUSIE_PIP, res$ifcausal, main = "SUSIE PIP")
  cp_plot(res$SUSIE_PIP_null, res$ifcausal, main = "SUSIE PIP null")
  cp_plot(res$SUSIE_PIP_w0, res$ifcausal, main = "SUSIE PIP weighted null")
}

caliFDR_plot <- function(tags, tag2){

  f <- lapply(tags, get_files, tag2 = tag2)
  gwasf <- lapply(f, '[[', "ggwas")
  names(gwasf) <- tags

  .tagname <- function(x, flist, colnames = NULL){
    a <- read.table(flist[[x]], header =T)
    if (!is.null(colnames)){
      colnames(a) <- colnames
    }
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }

  .addFDR <- function(res){
    res$FDR <- p.adjust(res$PVALUE, method = "fdr")
    res
  }

  gwasres <- do.call(rbind, lapply(lapply(tags, .tagname, flist = gwasf, 
                                   colnames =  c("chr",	"p0",	"p1", "name", 
                                                 "Estimate", "Std.Error", "t-value", "PVALUE")), .addFDR))

  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- merge(res, gwasres, by = "name", all = T)

  res <- res[complete.cases(res),]

  cp_plot(res$FDR, res$ifcausal, mode ="FDR", main = "TWAS FDR")
  cat("FDR at Bonferroni corrected p = 0.05: ", 1 - mean(res[res$PVALUE < 0.05 /dim(res)[1], "ifcausal"]))
}
```

@@

# PIP scatter plot
mr.ash2s PIP vs. susie PIP.
```{r scatterplot}
scatter_plot_PIP<- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- res[complete.cases(res),]
  res <- rename(res, c("PIP" = "mr.ash_PIP", "pip" = "SUSIE_PIP", "pip.null" = "SUSIE_PIP_null", "pip.w0" = "SUSIE_PIP_w0") )
  res$ifcausal <- mapvalues(res$ifcausal, 
          from=c(0,1), 
          to=c("Non causal", "Causal"))

  fig1 <- plot_ly(data = res, x = ~ mr.ash_PIP, y = ~ SUSIE_PIP, color = ~ ifcausal, 
                 colors = c( "salmon", "darkgreen"))

  fig2 <- plot_ly(data = res, x = ~ mr.ash_PIP, y = ~ SUSIE_PIP_null, color = ~ ifcausal, 
                 colors = c( "salmon", "darkgreen"))

  fig3 <- plot_ly(data = res, x = ~ mr.ash_PIP, y = ~ SUSIE_PIP_w0, color = ~ ifcausal, 
                 colors = c( "salmon", "darkgreen"))

  fig <- subplot(fig1, fig2, fig3, titleX = TRUE, titleY = T, margin = 0.05)
  fig
}
```
## NULL; expr-snp; expr-snp 
```{r sca 1, fig.height=3, fig.width=10}
scatter_plot_PIP(tags, tag2s[1])
```
## NULL; snp-expr; expr-snp

```{r sca 2, fig.height=3, fig.width=10}
scatter_plot_PIP(tags, tag2s[2])
```
## lasso; expr-snp; expr-snp

@@

# ROC curve
```{r roc}
ROC_plot<- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  gwasf <- lapply(f, '[[', "ggwas")
  names(gwasf) <- tags

  .tagname <- function(x, flist, colnames = NULL){
    a <- read.table(flist[[x]], header =T)
    if (!is.null(colnames)){
      colnames(a) <- colnames
    }
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))
  gwasres <- do.call(rbind, lapply(tags, .tagname, flist = gwasf, 
                                   colnames =  c("chr",	"p0",	"p1", "name", "Estimate", "Std.Error", "t-value", "PVALUE")))

  res <- merge(mrashres, susieres, by = "name", all = T)
  res <- merge(res, gwasres, by = "name", all = T)

  res <- res[complete.cases(res),]
  res <- rename(res, c("PIP" = "mr.ash", "pip" = "SUSIE", "pip.null"= "SUSIE.null", "pip.w0" = "SUSIE.w0", "PVALUE" = "TWAS") )
  res[,"TWAS"] <- -log10(res[, "TWAS"])

  roccolors <-  c("red", "green", "orange", "pink", "blue")
  methods <- c("mr.ash", "SUSIE", "SUSIE.null", "SUSIE.w0", "TWAS")
  plot(0, xlim=c(0,1), ylim=c(0,1), col="white", xlab = "FPR", ylab = "TPR")
  for (i in 1:length(methods)){
    method <- methods[i]
    bordered <- res[order(res[,method]),] 
    actuals <- bordered$ifcausal == 1
    sens <- (sum(actuals) - cumsum(actuals))/sum(actuals)
    spec <- cumsum(!actuals)/sum(!actuals)
    lines(1 - spec, sens, type = "l", col = roccolors[i])
    abline(c(0,0),c(1,1))
    auc <- sum(spec*diff(c(0, 1 - sens)))
    cat("AUC for ", method, ": ", auc)
  }
  legend(0.6,0.3, legend= methods, col=roccolors, lty=1, cex=0.5 )
  grid()
}
```

>>>>

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/sa2_default/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/sa2_default/"
tags <- paste0('20200721-1-', c(2, 4:9))
tagglob <- '20200721-1-*'
tagextr <- '20200721-1-\\d+'
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

# Mr.ash2 parameter estimation

@@

@@

# PIP calibration
We run 50 simulations and combine results.

@@

# PIP scatter plot
mr.ash2s PIP vs. susie PIP.

## NULL; expr-snp; expr-snp 
```{r sca 1, fig.height=3, fig.width=10}
scatter_plot_PIP(tags, tag2s[1])
```

```{r sca 2, fig.height=3, fig.width=10}
scatter_plot_PIP(tags, tag2s[2])
```

@@

# ROC curve

### 2020-08-05 analysis/simulation-multi-ukbchr17to22-gtex.adipose_sa2_v2.Rmd
move code-  plot functions

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/"
tags <- paste0('20200721-1-', 1:7)
tagglob <- '20200721-1-*'
tagextr <- '20200721-1-\\d+'
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

```{r getfile function}

get_files <- function(tag, tag2){
  par <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt")
  rpip <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".rPIP.txt")

  gmrash <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt")
  smrash <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt")

  ggwas <- paste0(outputdir, tag, ".exprgwas.txt.gz")
  sgwas <- paste0(outputdir, tag, ".snpgwas.txt.gz")

  gsusie <- paste0(susiedir, tag, ".", tag2, ".L3.susieres.expr.txt")
  ssusie <- paste0(susiedir, tag, ".", tag2, ".L3.susieres.snp.txt")

  return(tibble::lst(par, rpip, gmrash, ggwas, smrash, sgwas, gsusie, ssusie))
}

get_tags <- function(globpattern, extrpattern, tag2){
  lapply(lapply(get_files(globpattern, tag2), Sys.glob), str_extract, pattern = extrpattern)
}
```
# Mr.ash2 parameter estimation

@@

# PIP calibration
We run 50 simulations and combine results.
```{r caliplot}
#' s is pip or fdr.
cp_plot <- function(s, ifcausal, mode = c("PIP", "FDR"), main = mode[1]){
  # ifcausal:0,1
  a_bin <- cut(s, breaks= seq(0,1, by=0.1))
  if (mode == "PIP") {
     expected = c(by(s, a_bin, FUN = mean))
     observed = c(by(ifcausal, a_bin, FUN = mean))
  } else if (mode == "FDR"){
     expected = c(by(s, a_bin, FUN = mean))
     observed = 1 - c(by(ifcausal, a_bin, FUN = mean))
  }
  plot(expected, observed, xlim= c(0,1), ylim=c(0,1), pch =19, main = main)
  lines(x = c(0,1), y = c(0,1), col ="red")
}

caliPIP_plot <- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- res[complete.cases(res),]
  res <- rename(res, c("PIP" = "mr.ash_PIP", "pip" = "SUSIE_PIP", "pip.null" = "SUSIE_PIP_null", "pip.w0" = "SUSIE_PIP_w0"))
  par(mfrow=c(1,4), mar=c(5, 6, 4, 1))
  cp_plot(res$mr.ash_PIP, res$ifcausal, main = "Mr.ash PIP")
  cp_plot(res$SUSIE_PIP, res$ifcausal, main = "SUSIE PIP")
  cp_plot(res$SUSIE_PIP_null, res$ifcausal, main = "SUSIE PIP null")
  cp_plot(res$SUSIE_PIP_w0, res$ifcausal, main = "SUSIE PIP weighted null")
}

caliFDR_plot <- function(tags, tag2){

  f <- lapply(tags, get_files, tag2 = tag2)
  gwasf <- lapply(f, '[[', "ggwas")
  names(gwasf) <- tags

  .tagname <- function(x, flist, colnames = NULL){
    a <- read.table(flist[[x]], header =T)
    if (!is.null(colnames)){
      colnames(a) <- colnames
    }
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }

  .addFDR <- function(res){
    res$FDR <- p.adjust(res$PVALUE, method = "fdr")
    res
  }

  gwasres <- do.call(rbind, lapply(lapply(tags, .tagname, flist = gwasf, 
                                   colnames =  c("chr",	"p0",	"p1", "name", 
                                                 "Estimate", "Std.Error", "t-value", "PVALUE")), .addFDR))

  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- merge(res, gwasres, by = "name", all = T)

  res <- res[complete.cases(res),]

  cp_plot(res$FDR, res$ifcausal, mode ="FDR", main = "TWAS FDR")
  cat("FDR at bonferroni corrected p = 0.05: ", 1 - mean(res[res$PVALUE < 0.05 /dim(res)[1], "ifcausal"]))
}
```

@@

# PIP scatter plot
mr.ash2s PIP vs. susie PIP.
```{r scatterplot}
scatter_plot_PIP<- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- res[complete.cases(res),]
  res <- rename(res, c("PIP" = "mr.ash_PIP", "pip" = "SUSIE_PIP", "pip.null" = "SUSIE_PIP_null", "pip.w0" = "SUSIE_PIP_w0") )
  res$ifcausal <- mapvalues(res$ifcausal, 
          from=c(0,1), 
          to=c("Non causal", "Causal"))

  fig1 <- plot_ly(data = res, x = ~ mr.ash_PIP, y = ~ SUSIE_PIP, color = ~ ifcausal, 
                 colors = c( "salmon", "darkgreen"))

  fig2 <- plot_ly(data = res, x = ~ mr.ash_PIP, y = ~ SUSIE_PIP_null, color = ~ ifcausal, 
                 colors = c( "salmon", "darkgreen"))

  fig3 <- plot_ly(data = res, x = ~ mr.ash_PIP, y = ~ SUSIE_PIP_w0, color = ~ ifcausal, 
                 colors = c( "salmon", "darkgreen"))

  fig <- subplot(fig1, fig2, fig3, titleX = TRUE, titleY = T, margin = 0.05)
  fig
}
```
## NULL; expr-snp; expr-snp 
```{r sca 1, fig.height=3, fig.width=10}
scatter_plot_PIP(tags, tag2s[1])
```
## NULL; snp-expr; expr-snp

>>>>

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200721/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200721/"
tags <- paste0('20200721-1-', 1:7)
tagglob <- '20200721-1-*'
tagextr <- '20200721-1-\\d+'
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

# Mr.ash2 parameter estimation

@@

# PIP calibration
We run 50 simulations and combine results.

@@

# PIP scatter plot
mr.ash2s PIP vs. susie PIP.

## NULL; expr-snp; expr-snp 
```{r sca 1, fig.height=3, fig.width=10}
scatter_plot_PIP(tags, tag2s[1])
```
## NULL; snp-expr; expr-snp

### 2020-08-05 analysis/simulation-multi-ukbchr22-gtex.adipose2.Rmd
move code-  plot functions

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200616/"
tags <- paste0('20200616-8-', 1:9)
tagglob <- '20200616-8-*'
tagextr <- '20200616-8-\\d+'
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

```{r getfile function}
get_files <- function(tag, tag2){
  par <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".param.txt")
  rpip <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".rPIP.txt")

  gmrash <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".expr.txt")
  smrash <- paste0(outputdir, tag, "-mr.ash2s.", tag2, ".snp.txt")

  ggwas <- paste0(outputdir, tag, ".exprgwas.txt.gz")
  sgwas <- paste0(outputdir, tag, ".snpgwas.txt.gz")

  gsusie <- paste0(susiedir, tag, ".", tag2, ".L3.susieres.expr.txt")
  ssusie <- paste0(susiedir, tag, ".", tag2, ".L3.susieres.snp.txt")

  return(tibble::lst(par, rpip, gmrash, ggwas, smrash, sgwas, gsusie, ssusie))
}

get_tags <- function(globpattern, extrpattern, tag2){
  lapply(lapply(get_files(globpattern, tag2), Sys.glob), str_extract, pattern = extrpattern)
}
```
# Mr.ash2 parameter estimation
Results for 9 simulations runs, using different initiate and update strategy
```{r param function}
show_param <- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  parf <- lapply(f, '[[', "par")
  param <- do.call(rbind, lapply(parf, function(x) t(read.table(x))[2:1,]))
  truth <- param[1:(nrow(param)/2)*2-1,]
  est <- param[1:(nrow(param)/2)*2,]
  outdt <- matrix(0, ncol = 2*ncol(param), nrow = nrow(param)/2)
  outdt[,c(1,3,5,7)] <- truth
  outdt[,c(2,4,6,8)] <- est
  outdt <-cbind(1:nrow(outdt),outdt)
  colnames(outdt) <- c("Simulation#", paste0(rep(c("Truth","Est."),4)))
  knitr::kable(outdt) %>%
  kable_styling("striped") %>%
  add_header_above(c(" " = 1, "Gene.pi1" = 2, "Gene.PVE" = 2, "SNP.pi1" = 2, "SNP.PVE" =2))
}
```

@@

# PIP calibration
We run 100 simulations and combine results.
```{r caliplot}
#' s is pip or fdr.
cp_plot <- function(s, ifcausal, mode = c("PIP", "FDR"), main = mode[1]){
  # ifcausal:0,1
  a_bin <- cut(s, breaks= seq(0,1, by=0.1))
  if (mode == "PIP") {
     expected = c(by(s, a_bin, FUN = mean))
     observed = c(by(ifcausal, a_bin, FUN = mean))
  } else if (mode == "FDR"){
     expected = c(by(s, a_bin, FUN = mean))
     observed = 1 - c(by(ifcausal, a_bin, FUN = mean))
  }
  plot(expected, observed, xlim= c(0,1), ylim=c(0,1), pch =19, main = main)
  lines(x = c(0,1), y = c(0,1), col ="red")
}

caliPIP_plot <- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- res[complete.cases(res),]
  res <- rename(res, c("PIP" = "mr.ash_PIP", "pip" = "SUSIE_PIP", "pip.null" = "SUSIE_PIP_null", "pip.w0" = "SUSIE_PIP_w0"))
  par(mfrow=c(1,4), mar=c(5, 6, 4, 1))
  cp_plot(res$mr.ash_PIP, res$ifcausal, main = "Mr.ash PIP")
  cp_plot(res$SUSIE_PIP, res$ifcausal, main = "SUSIE PIP")
  cp_plot(res$SUSIE_PIP_null, res$ifcausal, main = "SUSIE PIP null")
  cp_plot(res$SUSIE_PIP_w0, res$ifcausal, main = "SUSIE PIP weighted null")
}

caliFDR_plot <- function(tags, tag2){

  f <- lapply(tags, get_files, tag2 = tag2)
  gwasf <- lapply(f, '[[', "ggwas")
  names(gwasf) <- tags

  .tagname <- function(x, flist, colnames = NULL){
    a <- read.table(flist[[x]], header =T)
    if (!is.null(colnames)){
      colnames(a) <- colnames
    }
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }

  .addFDR <- function(res){
    res$FDR <- p.adjust(res$PVALUE, method = "fdr")
    res
  }

  gwasres <- do.call(rbind, lapply(lapply(tags, .tagname, flist = gwasf, 
                                   colnames =  c("chr",	"p0",	"p1", "name", 
                                                 "Estimate", "Std.Error", "t-value", "PVALUE")), .addFDR))

  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- merge(res, gwasres, by = "name", all = T)

  res <- res[complete.cases(res),]

  cp_plot(res$FDR, res$ifcausal, mode ="FDR", main = "TWAS FDR")
  cat("FDR at bonferroni corrected p = 0.05: ", 1 - mean(res[gwasres$PVALUE < 0.05 /dim(res)[1], "ifcausal"]))
}
```

@@

# PIP scatter plot
mr.ash2s PIP vs. susie PIP.
```{r scatterplot}
scatter_plot_PIP<- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  .tagname <- function(x, flist){
    a <- read.table(flist[[x]], header =T)
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))

  res <- merge(mrashres, susieres, by = "name", all = T)

  res <- res[complete.cases(res),]
  res <- rename(res, c("PIP" = "mr.ash_PIP", "pip" = "SUSIE_PIP", "pip.null" = "SUSIE_PIP_null") )
  res$ifcausal <- mapvalues(res$ifcausal, 
          from=c(0,1), 
          to=c("Non causal", "Causal"))

  fig1 <- plot_ly(data = res, x = ~ mr.ash_PIP, y = ~ SUSIE_PIP, color = ~ ifcausal, 
                 colors = c( "salmon", "darkgreen"))

  fig2 <- plot_ly(data = res, x = ~ mr.ash_PIP, y = ~ SUSIE_PIP_null, color = ~ ifcausal, 
                 colors = c( "salmon", "darkgreen"))

  fig <- subplot(fig1, fig2, titleX = TRUE, titleY = T, margin = 0.1)
  fig
}
```
## NULL; expr-snp; expr-snp 
```{r sca 1, fig.height=4, fig.width=10}
scatter_plot_PIP(tags = tags, tag2 = tag2s[1])
```

@@

# ROC curve
```{r roc}
ROC_plot<- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  mrashf <- lapply(f, '[[', "gmrash")
  names(mrashf) <- tags

  susief <- lapply(f, '[[', "gsusie")
  names(susief) <- tags

  gwasf <- lapply(f, '[[', "ggwas")
  names(gwasf) <- tags

  .tagname <- function(x, flist, colnames = NULL){
    a <- read.table(flist[[x]], header =T)
    if (!is.null(colnames)){
      colnames(a) <- colnames
    }
    a[, "name"] <- paste0(x, ":", a[, "name"])
    a
  }
  mrashres <- do.call(rbind, lapply(tags, .tagname, flist = mrashf))
  susieres <- do.call(rbind, lapply(tags, .tagname, flist = susief))
  gwasres <- do.call(rbind, lapply(tags, .tagname, flist = gwasf, 
                                   colnames =  c("chr",	"p0",	"p1", "name", "Estimate", "Std.Error", "t-value", "PVALUE")))

  res <- merge(mrashres, susieres, by = "name", all = T)
  res <- merge(res, gwasres, by = "name", all = T)

  res <- res[complete.cases(res),]
  res <- rename(res, c("PIP" = "mr.ash", "pip" = "SUSIE", "PVALUE" = "TWAS") )
  res[,"TWAS"] <- -log10(res[, "TWAS"])

  roccolors <-  c("red", "green", "blue")
  methods <- c("mr.ash", "SUSIE", "TWAS")
  plot(0, xlim=c(0,1), ylim=c(0,1), col="white", xlab = "FPR", ylab = "TPR")
  for (i in 1:3){
    method <- methods[i]
    bordered <- res[order(res[,method]),] 
    actuals <- bordered$ifcausal == 1
    sens <- (sum(actuals) - cumsum(actuals))/sum(actuals)
    spec <- cumsum(!actuals)/sum(!actuals)
    lines(1 - spec, sens, type = "l", col = roccolors[i])
    abline(c(0,0),c(1,1))
    auc <- sum(spec*diff(c(0, 1 - sens)))
    cat("AUC for ", method, ": ", auc)
  }
  legend(0.6,0.3, legend= methods, col=roccolors, lty=1, cex=0.8)
  grid()
}
```

>>>>

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
library(kableExtra)
source("analysis/summarize_twas_plots.R")
```
```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
outputdir <- "~/causalTWAS/simulations/simulation_ashtest_20200616/"
susiedir <- "~/causalTWAS/simulations/simulation_susietest_20200616/"
tags <- paste0('20200616-8-', 1:9)
tagglob <- '20200616-8-*'
tagextr <- '20200616-8-\\d+'
tag2s <- c('zeroes-es', 'zerose-es', 'lassoes-es','lassoes-se')
```

# Mr.ash2 parameter estimation
Results for 9 simulations runs, using different initiate and update strategy
```{r param function}
show_param <- function(tags, tag2){
  f <- lapply(tags, get_files, tag2 = tag2)
  parf <- lapply(f, '[[', "par")
  param <- do.call(rbind, lapply(parf, function(x) t(read.table(x))[2:1,]))
  truth <- param[1:(nrow(param)/2)*2-1,]
  est <- param[1:(nrow(param)/2)*2,]
  outdt <- matrix(0, ncol = 2*ncol(param), nrow = nrow(param)/2)
  outdt[,c(1,3,5,7)] <- truth
  outdt[,c(2,4,6,8)] <- est
  outdt <-cbind(1:nrow(outdt),outdt)
  colnames(outdt) <- c("Simulation#", paste0(rep(c("Truth","Est."),4)))
  knitr::kable(outdt) %>%
  kable_styling("striped") %>%
  add_header_above(c(" " = 1, "Gene.pi1" = 2, "Gene.PVE" = 2, "SNP.pi1" = 2, "SNP.PVE" =2))
}
```

@@

# PIP calibration
We run 100 simulations and combine results.

@@

# PIP scatter plot
mr.ash2s PIP vs. susie PIP.

## NULL; expr-snp; expr-snp 
```{r sca 1, fig.height=4, fig.width=10}
scatter_plot_PIP(tags = tags, tag2 = tag2s[1])
```

@@

# ROC curve
